Community-Conditioned Language Models

### 2020-11-18 paper/paper.tex
info gain table/plot

>>>>

On the other hand, when we consider the \emph{information gain}\bn{define earlier}
of the CCLM over the corresponding (same encoder architecture)
un-conditioned

\begin{figure}
  \pplscatter{lstm-3-1_gain}{lstm-3-1_lmcc}
  \caption{%
    Mean community-wise information gain (x-axis) 
    and indiscernibility (y-axis) 
    %(Pearson's r = \num{0.16}; p = \num{0.2991}).  
    Shown here for the LSTM with $c = 1$.}
  \label{fig:cclm_lmcc_ppl}
\end{figure}

\begin{table}
  \centering
  \input{floats/lmcc_gain.tex}
  \caption{
    Pearson's r correlation between community-wise information gain (of the CCLM over the un-conditioned model) and indescernibility.
  }
  \label{tab:lmcc_gain}
\end{table}
